---
title: "VisaLimbo"
author: "parthkhare"
date: 2022-07-15T21:13:14-05:00
# categories: ["R"]
# tags: ["Immigration", "Visa", "Embassy"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(data.table);library(readxl);library(ggplot2); library(countrycode)
```

### Visa wait times
Coivd lockdowns are more or less over. With almost 70% of global population [vaccinated](%22https://www.nytimes.com/interactive/2021/world/covid-vaccinations-tracker.html%22), most countries have opened their borders. But can anyone really travel ? The waiting times to get any category of visa is unimaginably long. 


Based on State Department [data](https://travel.state.gov/content/travel/en/us-visas/visa-information-resources/wait-times.html), the following post analyses visa wait times for 237 embassies across 172 countries. There results are shown for three categories, Visitor Visa, Student/Exchange Visitor Visas and All Other Non-immigrant visa. 


Delay for Visitor visas is the highest, based on July, 2022 average delay is around 237 days. Following embassies currently have visitor's visa wait time for over 1 year

```{r, echo=FALSE, warning=FALSE, message=F}
# Scraped Data Stats
# --------------
scpdt_base <- read.csv('/Users/moonlight/Documents/Moonlight Projects/2022/Visa Limbo/Data/visascraped_base_mapped.csv')
scpdt_base$X <- NULL
scpdt_base <- data.table(scpdt_base)
scpdt_base$ctyname <- countrycode(scpdt_base$Country, origin = 'iso3c', destination = 'country.name')

# ----------------------------------------
# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$VisitorVisa>365,], aes(y=reorder(Embassy,VisitorVisa), 
                                                  x=VisitorVisa)) +
  geom_bar(fill='red',stat='identity') + ggtitle("Visitor Visa > 1 year") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))

```

Average delay for Student/Exchange Visitor Visas is 46 days, following are the embassies with maximum lags
```{r scpdt_base, echo=FALSE, warning=FALSE, message=F}

# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$Student_ExchangeVisitorVisas>60,], aes(y=reorder(Embassy,Student_ExchangeVisitorVisas), 
                                                  x=Student_ExchangeVisitorVisas)) +
  geom_bar(fill='darkgreen',stat='identity') + ggtitle("Student/Exchange Visitor Visas") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))
```



Average delay for All Other Non-immigrant Visas is 68 days, following are countries with longest delays
```{r, echo=FALSE, warning=FALSE, message=F}
# Scraped Data Stats
# --------------


# ----------------------------------------
# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$AllOtherNonimmigrantVisas>100,], aes(y=reorder(Embassy,AllOtherNonimmigrantVisas), 
                                                  x=AllOtherNonimmigrantVisas)) +
  geom_bar(fill='darkblue',stat='identity') + ggtitle("All Other Nonimmigrant Visas") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))
```




Questions?
Contact: visalimbo@gmail.com

